Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
comment on threat model; minor change on packet size distribution

The censor must operate at line rate; that is,
it must not delay traffic unduly while deciding whether to allow it.
This consideration is one facet of the censor's sensistivity to
collateral damage caused by false positives:
mistakenly blocking or degrading non-circumvention traffic causes the censor
to incur some penalty, just as mistakenly allowing circumvention traffic does.
The censor must allow TLS connections; meek does not try to look like plaintext.

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The three parts that are new in our system are:
\begin{enumerate}
\item The client program \meekclient.
Using the pluggable transports protocol, tor treats \meekclient\ as a SOCKS proxy.
When \meekclient\ receives data from tor, it bundles it up in an HTTP POST
request and sends it to the web app,
using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to tor.
\item The ``reflector'' web app, running on App Engine.
Its domain name \mbox{meek-reflect.appspot.com} is protected by domain fronting.
It is called a reflector because it doesn't do anything intelligent:
it merely copies the HTTP requests it receives and forwards them
to \meekserver\ running on the Tor bridge.
\item The server program \meekserver, which acts as an HTTP server.
It receives reflected requests from the web app, decodes their bodies,
and forwards the contents to an instance of tor running on the same host.
If there is anything pending to be sent back to the client,
\meekserver\ sends it along with its HTTP response.
\meekserver\ also takes care of stringing together multiple HTTP requests
into one logical stream and multiplexing multiple concurrent connections,
both using the technique of session IDs described in this section.
\end{enumerate}

@@

The main technical challenge in making this system work
is in encoding a TCP stream as a sequence of HTTP requests and responses.
\meekserver\ handles many clients at once, and their data streams
are split across multiple HTTP transactions.
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but we cannot do that because streams are split across multiple TCP sessions.
Rather, each instance of \meekclient\ generates at startup a random 32-byte
session ID, which is sent along with its requests in a special
X-Session-ID HTTP header.
\meekserver, when it sees a particular session ID for the first time,
opens up a new connection to the local tor process,
and stores the session ID in a cache. Subsequent requests with the
same session ID will reuse the same tor connection.
Entries are removed from the cache after a period of inactivity.

@@

% 1. TCP payload length
% 2. Number of concurrent connections
% 3. Connection Lifetime

% Conclusion:
% 1. long-lived connections with bulk data transfer may be suspicious
% 2. Distribution of packet sizes

@@

\paragraph{TCP payload length}
Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
figures exhibit a significant amount of packets with no payload. Most likely these packets are TCP SYN and ACK
packets. Figure \ref{fig:len:lbl} is the distribution of normal traffic, which indicates a large portion
of small-sized packets. While in the distribution of meek traffic shown in Figure \ref{fig:len:meek}, most packets
are large packets ranging from 1400B to 1500B.

@@

These browser techniques improve performance, but also lead to unexpected risks. The censor may be aware of the 
deviation from the distribution of normal traffic. Additionally, the persistent connection itself can be a problem.
We thus investigated other related characteristics.

@@

The distribution of meek traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user may already obtained the forbidden data she wants, or 
meek could simply restart a connection.

\paragraph{Conclusion} So far we have found two potential weaknesses: long-lived connections with bulk data transfer, 
and deviated distribution of packet sizes. To fundamentally fix these weaknesses we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what
is the model of normal traffic, which is an open problem. However, the arm-race game is symmetric; since finding a right
model is a difficult task for us, it is also difficult for the censor. Therefore, the censor can only find ad-hoc 
characteristics to block forbidden traffic, which are relatively easy to defend against.

>>>>

The censor must operate at line rate; that is,
it must not delay traffic unduly while deciding whether to allow it.
This consideration is one facet of the censor's sensistivity to
collateral damage caused by false positives:
mistakenly blocking or degrading non-circumvention traffic causes the censor
to incur some penalty, just as mistakenly allowing circumvention traffic does.
The censor must allow TLS connections; meek does not try to look like plaintext.
% but the censor may look at TLS characteristics and block suspicious connections.

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The three parts that are new in our system are:
\begin{enumerate}
\item The client program \meekclient.
Using the pluggable transports protocol, Tor treats \meekclient\ as a SOCKS proxy.
When \meekclient\ receives data from Tor, it bundles it up in an HTTP POST
request and sends it to the web app,
using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to Tor.
\item The ``reflector'' web app, running on App Engine.
Its domain name \mbox{meek-reflect.appspot.com} is protected by domain fronting.
It is called a reflector because it doesn't do anything intelligent:
it merely copies the HTTP requests it receives and forwards them
to \meekserver\ running on the Tor bridge.
\item The server program \meekserver, which acts as an HTTP server.
It receives reflected requests from the web app, decodes their bodies,
and forwards the contents to an instance of Tor running on the same host.
If there is anything pending to be sent back to the client,
\meekserver\ sends it along with its HTTP response.
\meekserver\ also takes care of stringing together multiple HTTP requests
into one logical stream and multiplexing multiple concurrent connections,
both using the technique of session IDs described in this section.
\end{enumerate}

@@

The main technical challenge in making this system work
is in encoding a TCP stream as a sequence of HTTP requests and responses.
\meekserver\ handles many clients at once, and their data streams
are split across multiple HTTP transactions.
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but we cannot do that because streams are split across multiple TCP sessions.
Rather, each instance of \meekclient\ generates at startup a random 32-byte
session ID, which is sent along with its requests in a special
X-Session-ID HTTP header.
\meekserver, when it sees a particular session ID for the first time,
opens up a new connection to the local Tor process,
and stores the session ID in a cache. Subsequent requests with the
same session ID will reuse the same Tor connection.
Entries are removed from the cache after a period of inactivity.

@@

@@

\paragraph{TCP payload length}
Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
of small-sized packets. However, in the meek traffic shown in Figure \ref{fig:len:meek}, most packets
are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
distribution. Therefore, meek provides traffic shaping without additional efforts.

@@

These browser techniques improve performance, but may also lead to unexpected consequences. 
Although meek alters the packet size distribution of underlying Tor traffic, 
the censor may be aware of the distribution of meek itself. 
Additionally, the persistent connection itself can be a problem.
We thus investigated other related characteristics.

@@

The distribution of meek traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.

\paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
distinguishing the meek traffic. But admittedly there two potential weaknesses: long-lived connections 
with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what is the model of normal traffic, which is an open problem. However, 
the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
easy to defend against.
